curiobaby_drop model analysis

### 2021-01-22 analysis/model_analysis_v2.Rmd

mdat <- mdat %>% rename(drop = drop_object,
                        target = target_object,
                        relation = condition) %>%
  mutate(drop = replace(drop, drop=="triangular_prism", "trig prism"),
         target = replace(target, target=="triangular_prism", "trig prism"))

@@

feat_names = names(mdat)[1:(ncol(mdat)-3)]
# for each feature, want to fit beta to maximize correlation between human and model choices
#feat_df <- get_feature_df(mdat, feat_names[1])

adult_fits = list()
for(feat in feat_names) {
  feat_df <- get_feature_df(mdat, feat)
  adult_fits[[feat]] = DEoptim(evalFit, lower=.01, upper=2, DEoptim.control(reltol=.001, NP=20, itermax=50), 
                feat_df=feat_df, hum_df=adult_trial_agg)
}
```

@@

child_fits = list()
for(feat in feat_names) {
  feat_df <- get_feature_df(mdat, feat)
  adult_fits[[feat]] = DEoptim(evalFit, lower=.01, upper=2, DEoptim.control(reltol=.001, NP=20, itermax=50), 
                feat_df=feat_df, hum_df=child_trial_agg)
}
```

>>>>

mdat <- mdat %>% rename(drop = drop_object,
                        target = target_object,
                        relation = condition) %>%
  mutate(drop = replace(drop, drop=="triangular_prism", "trig prism"),
         target = replace(target, target=="triangular_prism", "trig prism")) %>%
  select(-`obj_final_position_std_objects=drop`, -`obj_final_position_std_objects=target`)
# these cols are all 0...

@@

feat_names = names(mdat)[1:(ncol(mdat)-4)]
# for each feature, want to fit beta to maximize correlation between human and model choices
#feat_df <- get_feature_df(mdat, feat_names[1])

adult_fits = list()
for(feat in feat_names) {
  feat_df <- get_feature_df(mdat, feat)
  #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
  adult_fits[[feat]] = DEoptim(evalFit, lower=.01, upper=2, DEoptim.control(reltol=.001, NP=20, itermax=50), 
                feat_df=feat_df, hum_df=adult_trial_agg)
}
```

@@

child_fits = list()
for(feat in feat_names) {
  feat_df <- get_feature_df(mdat, feat)
  child_fits[[feat]] = DEoptim(evalFit, lower=.01, upper=2, DEoptim.control(reltol=.001, NP=30, itermax=50), 
                feat_df=feat_df, hum_df=child_trial_agg)
}
```

```{r}
adult_mfit <- tibble()
child_mfit <- tibble()

for(f in names(adult_fits)) {
  adult_mfit = bind_rows(adult_mfit, c(feature=f, 
                                       beta=as.numeric(unlist(adult_fits[[f]]$optim$bestmem)), 
                                       r=-adult_fits[[f]]$optim$bestval))
  child_mfit = bind_rows(child_mfit, c(feature=f, 
                                       beta=as.numeric(unlist(child_fits[[f]]$optim$bestmem)), 
                                       r=-child_fits[[f]]$optim$bestval))
}

adult_mfit <- adult_mfit %>% 
  mutate(beta = as.numeric(beta),
         r = as.numeric(r)) %>%
  arrange(desc(r))

adult_mfit
```

```{r children}
child_mfit <- child_mfit %>% 
  mutate(beta = as.numeric(beta),
         r = as.numeric(r)) %>%
  arrange(desc(r))

child_mfit
```
```{r}
save(mdat, child_mfit, adult_mfit, file=here("models/model_data.RData"))
```
